**Density Dependence**

### 2023-02-15 Rmd/report mac.Rmd
report.R & Rmd updated

@@

[to be done]

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_om_biomass_yield.jpg")))

@@

**Comparison of equilibrium curves for density dependence analyses: biomass against F**

fig_nums(
  name    = "om_eqf", level = 1, display = FALSE,
  caption = "Equilibrium curves for density dependence analyses: biomass against F")

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_om_biomass_F.jpg")))

_`r fig_nums("om_eqf")`_

<!-- =============================================================================================================== -->
<!-- Section 5: Running MSE's                                                                                        -->
<!-- =============================================================================================================== -->

# Running MSE's

>>>>

**Stock assessments**

@@

fig_nums(
  name    = "om_assessments", level = 1, display = FALSE,
  caption = "Comparison of different assessments. VPA-M is used going forward")

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_comparing_assessments.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_comparing_dd.jpg")))

@@

<!-- =============================================================================================================== -->
<!-- Section 5: Running forward projections                                                                          -->
<!-- =============================================================================================================== -->

# Forward projections without feedback
